SunPy - Python for Solar Physics

### 2014-08-28 2-3-Spectra.tex
more bug fixes, and finishes addressing #80

As with other SunPy data types, the \texttt{Spectrogram} class has been
built so that each instrument initialises using a subclass containing the instrument-specific 
functionalities. The common functionality provided by the base \texttt{Spectrogram} class includes
joining different time ranges and frequencies, performing frequency-dependent background subtraction,
and convenient visualization and sampling of the data.
Currently, the \texttt{Spectrogram} class supports radio spectrograms from the 
\href{http://www.e-callisto.org/}{e-Callisto}
solar radio spectrometer network \citep{2009EM&P..104..277B} and \textit{STEREO}/SWAVES spectrograms \citep{2008SSRv..136..487B}.

@@

\begin{listing}[H]
\pythoncode{pycode_spectra.txt}
\begin{center}
\includegraphics[width=0.8\columnwidth]{callisto_nobg}
\end{center}
\caption{Example of how \texttt{CallistoSpectrogram} retrieves the
  data for the requested time range and observatory, merges it, and
  removes the background signal.  The data requested -- `BIR' -- is
  the code name of the \href{http://www.rosseobservatory.ie}{Rosse Observatory}
  at Birr Castle in Ireland.}
\label{code:spectra}
\end{listing}

>>>>

As with other SunPy data types, the \texttt{Spectrogram} class has been
built so that each instrument initialises using a subclass containing the instrument-specific 
functionalities. The common functionality provided by the base \texttt{Spectrogram} class includes
joining different time ranges and frequencies, performing frequency-dependent background subtraction,
and convenient visualization and sampling of the data.
Currently, the \texttt{Spectrogram} class supports radio spectrograms from the e-Callisto (
\url{http://www.e-callisto.org/})
solar radio spectrometer network \citep{2009EM&P..104..277B} and \textit{STEREO}/SWAVES spectrograms \citep{2008SSRv..136..487B}.

@@

\begin{listing}[H]
\pythoncode{pycode_spectra.txt}
\begin{center}
\includegraphics[width=0.8\columnwidth]{callisto_nobg}
\end{center}
\caption{Example of how \texttt{CallistoSpectrogram} retrieves the
  data for the requested time range and observatory, merges it, and
  removes the background signal.  The data requested -- `BIR' -- is
  the code name of the Rosse Observatory \url{http://www.rosseobservatory.ie}
  at Birr Castle in Ireland.}
\label{code:spectra}
\end{listing}

### 2014-08-28 3-3-HELIO.tex
more bug fixes, and finishes addressing #80

\begin{listing}[h]
\pythoncode{pycode_helio.txt}
\caption{Example of querying the HEC service to multiple CME
catalogues, in this case the ones detected automatically 
by \href{http://sidc.oma.be/cactus/}{CACTus} \citep{robbrecht2009}.}
\label{code:helio}
\end{listing}

>>>>

\begin{listing}[h]
\pythoncode{pycode_helio.txt}
\caption{Example of querying the HEC service to multiple CME
catalogues, in this case the ones detected automatically 
by the Computer Aided CME Tracking feature recognition algorithm CACTus (\url{http://sidc.oma.be/cactus/}) \citep{robbrecht_automated_2009}.}
\label{code:helio}
\end{listing}

### 2014-08-28 3-5-Database.tex
more bug fixes, and finishes addressing #80

The \texttt{database} subpackage can make use of any database software supported by
{\texttt{SQLAlchemy} (\href{http://www.sqlalchemy.org}{http://www.sqlalchemy.org}). This library was chosen
since it supports many SQL dialects. 
If SQLite is selected, the database is stored as a single file, which is
created automatically. A server-based database, on the other hand, could be used
by collaborators who work together on the
same data from different computers: a central database server stores all data and the clients connect to
it to read or write data.

>>>>

The \texttt{database} subpackage can make use of any database software supported by
{\texttt{SQLAlchemy} (\url{http://www.sqlalchemy.org}). This library was chosen
since it supports many SQL dialects. 
If SQLite is selected, the database is stored as a single file, which is
created automatically. A server-based database, on the other hand, could be used
by collaborators who work together on the
same data from different computers: a central database server stores all data and the clients connect to
it to read or write data.
